Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-03-24 doc/paper.Rmd
added notes on wright 2006

-   @mulkey1996 and @bonal2016 will have goods stuff; haven't looked them over yet\

>>>>

-   @mulkey1996 and @bonal2016 will have goods stuff; haven't looked them over yet

-   @wrightSeasonalNinoLonger2006: Increase in flower and seed production after El Niño events for trees and lianas.
    Might be due to increases solar irradiance.
    Maybe evidence of lagged effects?
    Table 2 is inconsistent with text, so not sure...

-   Many humid tropical forest species time reproduction to coincide with dry season peak to avoid low irradiance in wet season.
    (refs within @wrightSeasonalNinoLonger2006. van Shaik et al. 1993; Wright and vanSchaik 1994).
    So rather than bet-hedging, maybe extra dry dry seasons are actually just really prime conditions for *Heliconia* reproduction and recruitment.

-   \
